### 2012-12-04 inst/examples/policycosts/policycosts.Rmd
accompanying main source file for previous 3 commits

This file is called by `policycosts_writeup.Rmd`.  First it calibrates the apples-to-apples comparison level for each penalty function, and then generates sample plots by penalty function, illustrating the resulting stock dynamics and harvest quota dynamics.  The file needs a `profit` function to be specified and the grid of `c2` values over which we search to find the coefficient introducing the 25% reduction in Net Present Value (npv).

@@

@@

``` {r npv-plot, dependson="quadcosts"}
npv0 <- dat[1,3] 
npv0
dat <- data.frame(c2=c2,dat)
dat <- melt(dat, id="c2")
ggplot(dat, aes(c2, value, col=variable)) + geom_point() + geom_line()
````

@@

```{r apples_plot, dependson="quadcosts"}
ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
````

@@

```{r quad_costs, dependson="apples"}
quad_profit <- profit_harvest(price = 10, c0 = 30, c1 = apples["quad"]) 
quad_costs <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, quad_profit, delta, reward, penalty =  none)
```

>>>>

This file is called by `policycosts_writeup.Rmd`.  First it calibrates the apples-to-apples comparison level for each penalty function, and then generates sample plots by penalty function, illustrating the resulting stock dynamics and harvest quota dynamics.

@@

```{r}
profit <- profit_harvest(price = price, c0 = c0, c1 = c1)
c2 <- exp(seq(0, log(21), length.out = 20))-1
```

@@

``` {r npv-plot, dependson="quadcosts"}
npv0 <- dat[1,3] 
npv0
dat <- data.frame(c2=c2,dat)
dat <- melt(dat, id="c2")
````

@@

```{r apples_plot, dependson="quadcosts"}
apples_plot <- ggplot(dat, aes(c2, (max(value)-value)/max(value), col=variable)) + geom_point() + geom_line()
````

@@

```{r quad_costs, dependson="apples"}
quad_profit <- profit_harvest(price = 10, c0 = c0, c1 = apples["quad"]) 
quad_costs <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, quad_profit, delta, reward, penalty =  none)
```
